Conditions for $d$-local-connectedness of boundaries of hyperbolic groups

### 2020-02-18 paper.tex
Moved (dG - xi simply connected => loc simp con)

\begin{proposition}
  If $\boundary G - \set\xi$ is connected for any $\xi \in \boundary G$ then
  $G$ satisfies $\ddag_M$ for any $M$.
\end{proposition}

@@

@@

@@

We now use the maps $i^n_\infty$ to construct homotopies in $\boudndary G$. To
begin, we prove the following proposition, which constructs homotopies between
certain special maps.

@@

\section{Simply connected point complements}
\todo{Move this section into section 3}

In this section we give a sufficient condition for the condition $\S_M$ to be
satisfied.

>>>>

\begin{proposition}\cite[Proposition ?]{bestvinamess91}\label{prop:BM2}
  If $\boundary G - \set\xi$ is connected for any $\xi \in \boundary G$ then
  $G$ satisfies $\ddag_M$ for any $M$.
\end{proposition}

@@

\subsection{A two-dimensional version}

@@

We can immediately give a sufficient condition for $\S_M$ to be satisfied. This
result is analagous to Proposition~\ref{prop:BM2}.

@@

We now use the maps $i^n_\infty$ to construct homotopies in $\boundary G$. To
begin, we prove the following proposition, which constructs homotopies between
certain special maps.

@@
